\section{Sprint Retrospective} % (fold)
\label{sec:Sprint Retrospective}

A number of things went relatively well for this sprint. Although there were a lot of obligations with regards to exams and other holiday-related obligations, we were still able to meet up and implement quite a bit of core functionality for the project flow system. Also, group members that had not had prior experience with our version control system Git, really got the hang of it and as a result productivity subsequently increased markedly. Using our chosen static analysis tool JSLint was surprisingly easy, taking only minutes to setup and run, and cleared the code up a lot. 

There were however also a number of areas where things went less well. Occasionally, a lot of time was wasted when erroneous code was committed to the main repository, causing some confusion. Also, branching/forking is still not being done, which lead to some troubles when merging different versions.

We can definitely improve on a number of things moving forward. We definitely need to meet more often, and on time to avoid work piling up towards the end of sprints. Also, we need more experience using git as a part of our development process, and commit discipline needs to improve. E.g. don't commit erroneous code, pull often etc. Another thing we need to improve on is using SCRUM, particularly we need to update the amount of time we spend during sprints more often. Finally, we should definitely continue to use static analysis tools to aid us moving forward. 

% section Sprint Retrospective (end)