\section{Sprint Retrospective} % (fold)
\label{sec:Sprint Retrospective}

In this sprint we tried to implement as much functionality as posible, given our limited time. Our main focus was to finish items that were half done, hard coded, and yielded most added functionality. The app is far from done, but several key components are nearing done state. \\
We did not meet with the product owner, during this sprint, but he was made aware of our progress and he approves of the result of the product implemented so far.

What went well:

\begin{itemize}
	
\item The app is packaged on PhoneGap and now runs with actual data.
\item The product owner likes the alpha release. The graphing tool was provided a simple interface to visualise data that product owner dowloaded from statistik banken and preliminary tests done by the product owner has been positive.
\item We finalized several loose ends from earlier sprints such as CSS styling,JavaScript controller handler, Gesture optimisation on charts etc.
\item Performance tweaks show improved results on tablets.
\item Working together for extended periods of time meant that we got more done.

\end{itemize}
What went bad:
\begin{itemize}
\item Task took more time that anticipated such as identifyoing jey ares which could improve performance significantly.
\item Project management tool which was conceptualised in the beginning was dropped because of time constraints.
\item Testing wasn't done thouroughly with unit tests, because our chosen test tool Siesta didn't allow us to access deeper parts of our functions in JavaScript, we do however have a unit test that shows that the larger scale parts are there.

\end{itemize}
% section Sprint Retrospective (end)